### 2015-09-10 fundamentals/abs.tex
helps with #116

\newpage
\begin{abstract}
As nuclear power expands, technical, economic, political, and environmental
analyses of nuclear fuel cycles by simulators increase in importance.  To date,
however, current tools are often rigid rather than flexible, fleet-based rather
than discrete, or privately distributed rather than open source. Each of these
choices presents a challenge to modeling fidelity, generality, efficiency,
robustness, and scientific transparency.  The \Cyclus nuclear fuel cycle
simulator framework and its modeling ecosystem incorporate modern insights from
simulation science and software architecture to solve these problems so that
challenges in nuclear fuel cycle analysis can be better addressed.  A summary
of the \Cyclus fuel cycle simulator framework and its modeling ecosystem are
presented. Additionally, the implementation of each is discussed in the context
of motivating challenges in nuclear fuel cycle simulation.  Finally, the
current capabilities of \Cyclus are demonstrated for both an open and a closed
fuel cycle.
\end{abstract}

>>>>

\begin{abstract}
As nuclear power expands, technical, economic, political, and environmental
analyses of nuclear fuel cycles by simulators increase in importance.  To date,
however, current tools are often fleet-based rather than discrete and privately
distributed rather than open source. Each of these choices presents a challenge
to modeling fidelity, generality, efficiency, robustness, and scientific
transparency.  The \Cyclus nuclear fuel cycle simulator framework and its
modeling ecosystem incorporate modern insights from simulation science and
software architecture to solve these problems so that challenges in nuclear
fuel cycle analysis can be better addressed.  A summary of the \Cyclus fuel
cycle simulator framework and its modeling ecosystem are presented.
Additionally, the implementation of each is discussed in the context of
motivating challenges in nuclear fuel cycle simulation.  Finally, the current
capabilities of \Cyclus are demonstrated for both open and closed fuel
cycles.
\end{abstract}
